\documentclass[a4paper,12pt,oneside, tikz]{book}  
\usepackage[utf8]{inputenc}
\usepackage{tcolorbox}
\usepackage{amsmath,amssymb,amsthm, enumitem, hyperref, tabto} 
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{wrapfig}
\usepackage{lastpage}
\usepackage{tikz}
\usetikzlibrary{external}
\tikzexternalize % activate!
\usepackage[american]{circuitikz}
\usepackage[absolute,overlay]{textpos}
\usepackage[left=2cm,right=2cm]{geometry}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{float}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Studio 4},
    pdfpagemode=FullScreen,
    }

\input{arduinoLanguage.tex}

\urlstyle{same}
\usepackage{xcolor}
\usepackage{colortbl}

\usepackage{listings}
\usepackage{xcolor}
\colorlet{mygray}{black!30}
\colorlet{mygreen}{green!60!blue}
\colorlet{mymauve}{red!60!blue}
\newcommand\inostyle{\lstset{
  backgroundcolor=\color{gray!10},  
  basicstyle=\ttfamily,
  columns=fullflexible,
  breakatwhitespace=false,      
  breaklines=true,                
  captionpos=b,                    
  commentstyle=\color{mygreen}, 
  extendedchars=true,              
  frame=single,                   
  keepspaces=true,
  keywordstyle=\color{blue},      
  language=Arduino,                 
  numbers=none,                
  numbersep=5pt,                   
  numberstyle=\tiny\color{blue}, 
  rulecolor=\color{mygray},        
  showspaces=false,               
  showtabs=false,                 
  stepnumber=5,                  
  stringstyle=\color{mymauve},    
  tabsize=3,                      
  title=\lstname                
}}

% INO environment
\lstnewenvironment{ino}[1][]
{
\inostyle
\lstset{#1}
}
{}


% Ino for external files
\newcommand\inoexternal[2][]{{
\inostyle
\lstinputlisting[#1]{#2}}}

% Ino for inline
\newcommand\inoinline[1]{{\inostyle\lstinline!#1!}}

\usepackage{minted}

\usepackage{graphicx, multicol, latexsym}
\usepackage{blindtext}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{capt-of}
\usepackage{tabu}
\usepackage{booktabs}

\usepackage{fancyhdr}            % Permits header customization. See header section below.
\fancypagestyle{plain}{
    \lhead{}
    \fancyhead[R]{\thepage}
    \fancyhead[L]{}
    \renewcommand{\headrulewidth}{0pt}
    \fancyfoot{}
}

\pagestyle{fancy}
\fancyhead[R]{\thepage}
\fancyhead[L]{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}

\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\usepackage{titlesec}

\titleformat{\chapter}[display]{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Huge}

% this alters "before" spacing (the second length argument) to 0
\titlespacing*{\chapter}{0pt}{0pt}{40pt}


\addto\captionsenglish{\renewcommand{\chaptername}{Activity}} 


\title{\Huge\textbf{Jump Starting ALEX} \\ \Large{CG2111A Studio Report}}

\author{
Kuek Yeau Hao Jonathan (A0258485M), \\
Leong Zhe Ming (A0252060W), \\
Tran Duc Khang (A0242247J), \\ 
Prannaya Gupta (A0242267E)
}

\begin{document}

\maketitle

\newpage

\textbf{Q1. Examine the code in \texttt{w8s2p3.ino} in the Arduino IDE. What do you think you are seeing in the output?} (2 MARKS)

\begin{tcolorbox}
\textbf{Solution:}\\
\texttt{\textbf{58}    char theSize = (char) sizeof(TData); \\
\textbf{59}    Serial.write(theSize); \\
\textbf{60}    Serial.write((char *) &test, sizeof(TData));} \\

\\

The code is trying to print the size of TData, but due to it being converted to a character, this is replaced with 'End of Transmission' (ASCII Character 4). After this, it is printing \texttt{x} and \texttt{y}, but they aren't rendered as ASCII Character 5 is 'Enquiry' and ASCII Character 10 is 'Line Feed', or rather newline.
\end{tcolorbox}

\textbf{Q2. Examine the values of \texttt{x} and \texttt{y} in \texttt{w8s2p3.ino}. Are the values the Pi is receiving correct?} (1 MARK)

\begin{tcolorbox}
The Pi received around \texttt{655365} for \texttt{x} and \texttt{-1092980228} for \texttt{y}, which are clearly incorrect.
\end{tcolorbox}

\textbf{Q3. Is \texttt{x} and \texttt{y} printing correctly now? What do you think caused \texttt{w8s2p3-pi} to print the incorrect answers in Question 1 above?} (3 MARKS)

\begin{tcolorbox}
Yes, it is printing correctly now. \\

The initial code for \texttt{w8s2p3-pi} reads both integers as double the bits, hence \texttt{x} received follows the following formula (following Little Endian):

$$x' = y \times 2^{16} + x = 655365$$

On the other hand, \texttt{y} gives a random value as it is undefined.
\end{tcolorbox}


\textbf{Q4. Take note of the size of \texttt{TData} on the Pi and on the Arduino. Is there a difference in size? Is this difference affecting the answers for \texttt{x} and \texttt{y}?} (3 MARKS)

\begin{tcolorbox}
The size of \texttt{TData} on the Pi is 6 bytes, while the size of \texttt{TData} on the Arduino is 5 bytes. Yes, this is affecting it as \texttt{y} and \texttt{x} are joined when reading from the Pi.
\end{tcolorbox}

\textbf{Q5. Are the \texttt{x}, \texttt{y} and \texttt{c} fields being printed correctly now? What does this tell you about how the \texttt{gcc} compiler on the Pi compile \texttt{TData} versus the compiler on the Arduino?} (3 MARKS)

\begin{tcolorbox}
Yes, it is now printed correctly. \\

This tells us that the \texttt{gcc} compiler pads the structure to keep every structure member of the same size, but the Arduino does no such thing.



\end{tcolorbox}

\begin{ino}

Studio Marks: ___________ / 12
\end{ino}

\end{document}